Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-02-20 Documents/Euler/Benchmarks1D/draft.tex
more wave types

\subsection{Test 9: Peak}
When finding density, method 1 falls considerably short of the maximum. On the pressure graph, method 3 features both a jump above and a dip below the graph between positions 0.1 and 0.2. Velocity shows a similar (but considerably larger) dip, followed by jump, in the vertical section of the graph between 0.1 and 0.2. Method 1 also overestimates the maximum velocity and is above both exact and method 3 in the middle horizontal section.

@@

Density, pressure, and velocity all show significant oscillations that follow the shock wave. These oscillations are not part of the exact solution, and appear to a different extend based on the integration method used. First order gives a few wide oscillations; higher order methods give more, taller, and thinner oscillations, with the third order giving the most. 
\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T10.png} &
	  \includegraphics[width=.4\textwidth]{den10zoom.png} \\
	  \includegraphics[width=.4\textwidth]{vel_T10.png} &	
	  \includegraphics[width=.4\textwidth]{vel10zoom.png} \\
      \includegraphics[width=.4\textwidth]{prs_T10.png} &	
      \includegraphics[width=.4\textwidth]{prs10zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{Results for test 10 at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line. Each pair of side-by-side panels shows the same results at different zoom levels. The top panels show density, the middle show velocity, and the bottom show pressure.}
\end{figure}

@@

\subsection{Test 11: Slow-moving Shock}
This test, like the previous one, shows significant oscilltions following the shock wave, particularly with higher order methods. However, these oscillations in the second and third order results appear to be more periodic than those in the previous test. 
\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T11.png} &
	  \includegraphics[width=.4\textwidth]{den11zoom.png} \\
	  \includegraphics[width=.4\textwidth]{vel_T11.png} &	
	  \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
      \includegraphics[width=.4\textwidth]{prs_T11.png} &	
      \includegraphics[width=.4\textwidth]{prs11zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{Results for test 11 at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line. Each pair of side-by-side panels shows the same results at different zoom levels. The top panels show density, the middle show velocity, and the bottom show pressure.}
\end{figure}

>>>>

\subsection{Test 9: Peak}
The peak problem features a shock wave at $x=0.554$, as well as a contact discontinuity at $x=0.546$. A rarefaction wave is also present between about $x=0.16$ and $x=0.2$. When finding density, method 1 falls considerably short of the maximum. On the pressure graph, method 3 features both a jump above and a dip below the graph between positions 0.1 and 0.2. Velocity shows a similar (but considerably larger) dip, followed by jump, in the vertical section of the graph between 0.1 and 0.2. Method 1 also overestimates the maximum velocity and is above both exact and method 3 in the middle horizontal section.

@@

In this problem, a shock wave is present at about $x=11$. Density, pressure, and velocity all show significant oscillations that follow the shock wave. These oscillations are not part of the exact solution, and appear to a different extend based on the integration method used. First order gives a few wide oscillations; higher order methods give more, taller, and thinner oscillations, with the third order giving the most. 
\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T10.png} &
	  \includegraphics[width=.4\textwidth]{den10zoom.png} \\
	  \includegraphics[width=.4\textwidth]{vel_T10.png} &	
	  \includegraphics[width=.4\textwidth]{vel10zoom.png} \\
      \includegraphics[width=.4\textwidth]{prs_T10.png} &	
      \includegraphics[width=.4\textwidth]{prs10zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{Results for test 10 at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line. Each pair of side-by-side panels shows the same results at different zoom levels. The top panels show density, the middle show velocity, and the bottom show pressure.}
\end{figure}

@@

\subsection{Test 11: Slow-moving Shock}
In this problem, a shock wave is present at about $x=0.5$.This test, like the previous one, shows significant oscilltions following the shock wave, particularly with higher order methods. However, these oscillations in the second and third order results appear to be more periodic than those in the previous test. 
\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T11.png} &
	  \includegraphics[width=.4\textwidth]{den11zoom.png} \\
	  \includegraphics[width=.4\textwidth]{vel_T11.png} &	
	  \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
      \includegraphics[width=.4\textwidth]{prs_T11.png} &	
      \includegraphics[width=.4\textwidth]{prs11zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{Results for test 11 at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line. Each pair of side-by-side panels shows the same results at different zoom levels. The top panels show density, the middle show velocity, and the bottom show pressure.}
\end{figure}
